Automatic discovery of cell types and microcircuitry from neural connectomics

### 2014-12-14 docs/paper.tex
text updates

\fxwarn{Do we talk about cross-validation early on? What about posterior uncertainty?}

@@

To test whether our model accurately captures the true structure of
the data, we learn the model on the data with a subset of the links
missing and then compute our predictive accuracy. We perform 10-way
cross validation on a given dataset, learn the resulting model, and
use that model to predict the missing synapses. Each potential
link between cells is assigned a probability, and we compute
the area under the curve (AUC) for the resulting ROC curve. 
\fxwarn{Add additional ARI} 
\section*{Results}

@@

\fxwarn{Add results}

@@

\fxwarn{Add ``intrudoce spatial structure where there is none}

@@

\subsection*{Microprocessor}
We extracted the connection graph for the transistors in the MOS6502
\autocite{visual6502source}. Each transistor has three terminals (gate,
source, drain), but the methods of the original dataset were unable to
consistently resolve which of the C1 and C2 terminals were source and
drain, leading to ambiguity in our encoding. We identified a region
consisting of three registers X, Y, and S via visual
inspection and focused our efforts there. We created a total of six
connectivity matrices by examining possible terminal pairings. One
graph, for example, $R^{gc_1}(e_i, e_j)=1$ if transistor $e_j$ and
$e_j$ are connected via pins $g$ and $c_1$.

>>>>

\fxwarning{Do we talk about cross-validation early on? What about
  posterior uncertainty?}

@@

To test whether our model accurately captures the true structure of
the data, we learn the model on the data with a subset of the links
missing and then compute our predictive accuracy. We perform 10-way
cross validation on a given dataset, learn the resulting model, and
use that model to predict the missing synapses. Each potential
link between cells is assigned a probability, and we compute
the area under the curve (AUC) for the resulting ROC curve. 
\fxwarning{Add additional ARI} 
\section*{Results}

@@

\fxwarning{Add results}

@@

\fxwarning{Add ``intrudoce spatial structure where there is none}

@@

### 2014-12-14 docs/processor.tex
text updates

>>>>

\subsection*{Microprocessor}
We extracted the connection graph for the transistors in the MOS6502
\autocite{visual6502source}. Each transistor has three terminals (gate,
source, drain), but the methods of the original dataset were unable to
consistently resolve which of the C1 and C2 terminals were source and
drain, leading to ambiguity in our encoding. We identified a region
consisting of three registers X, Y, and S via visual
inspection and focused our efforts there. We created a total of six
connectivity matrices by examining possible terminal pairings. One
graph, for example, $R^{gc_1}(e_i, e_j)=1$ if transistor $e_j$ and
$e_j$ are connected via pins $g$ and $c_1$.
